\documentclass[11pt]{article}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper,left=1.5cm,right=1.5cm,top=2cm,bottom=2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[sfdefault]{inter}

% --- Colors ---
\definecolor{accent}{HTML}{536878} % change if you want a different tint
\definecolor{muted}{HTML}{4C566A}

% --- Formatting ---
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt}

% --- Section style ---
\newcommand{\cvsection}[1]{%
  \vspace{6pt}%
  {\large\bfseries\textcolor{accent}{#1}}\\[-4pt]%
  \textcolor{accent}{\rule{\linewidth}{0.6pt}}%
  \vspace{6pt}%
}

% --- Small cventry macro for the article class ---
% Usage: \cventry{dates}{title}{organization}{location}{description-block}
\newcommand{\cventry}[5]{%
  {\textbf{#2}} \hfill {\small\textcolor{muted}{#1}}\\
  {\small\itshape #3} \hfill {\small\textcolor{muted}{#4}}\\[-6pt]
  #5
  \vspace{6pt}
}

\begin{document}

% ---------- Header ----------
\begin{center}
	{\Huge\bfseries Mahmoud Ayman Farouk Mohammed} \\[6pt]
	{\large\textcolor{accent}{DevOps \& SRE Engineer}} \\[8pt]
	Alexandria, Egypt \\[6pt]

	\href{mailto:mahmoud.a.asran@outlook.com}{mahmoud.a.asran@outlook.com}\quad • \quad
	\href{tel:+201091794795}{+20 109 179 4795} \\[6pt]

	\href{https://github.com/mahmoudk1000}{GitHub}\quad • \quad
	\href{https://www.linkedin.com/in/mahmoudk1000}{LinkedIn}\quad • \quad
	\href{https://mahmoudk1000.github.io/}{Blog}
\end{center}

\vspace{8pt}

% ---------- Profile ----------
\cvsection{Profile}
I build reliable systems and enjoy the engineering behind them. I’m a hands-on DevOps/SRE who values automation, observability, and the craft of building well-designed services that are maintainable, testable and pleasant to operate. I write infrastructure and runtime code — including services and tooling in \texttt{Go} — so I can transform ideas from prototype to production. I love solving problems, tinkering with Linux internals, designing CI/CD and operator-driven automation, and sharing improvements with the community. I also design processes that help teams deliver value consistently and sustainably. I bring effort and attention to detail, shipping work that I trust, want to run, and can maintain with confidence.

% ---------- Professional Experience ----------
\cvsection{Experience}

\cventry{Jul 2024 -- Present}{DevOps / SRE Engineer}{\href{https://atos.net}{Atos}}{Cairo, Egypt}{%
	\begin{itemize}
		\item Operate and improve Kubernetes clusters and surrounding environments to maintain reliability and scale.
		\item Build automation with PowerShell, Ansible, and Terraform to eliminate toil and standardize provisioning.
		\item Design and maintain CI/CD pipelines (Azure DevOps, GitHub Actions) to accelerate safe delivery and enforce quality gates.
		\item Build PoCs and introduce tools or patterns that address operational challenges and improve workflows or help business.
		\item Define SLIs and SLOs from SLAs; implement dashboards and alerts to measure compliance.
		\item Apply SRE practices: monitoring, alerting, and centralized logging (Prometheus, Grafana, ELK) to deliver SLAs.
		\item Troubleshoot incidents, identify root cause, isolate failures, and restore services.
		\item Mentor colleagues and interns; sharing knowledge.
	\end{itemize}
}

% To add more experiences, follow this pattern:
% \cventry{dates}{title}{\href{url}{company}}{location}{%
% 	\begin{itemize}
% 		\item Achievement or responsibility 1.
% 		\item Achievement or responsibility 2.
% 	\end{itemize}
% } \cite{experience-key}

% ---------- Open Source / Projects ----------
\cvsection{Open Source / Projects}

FOSS advocate and active contributor across cloud-native and tooling ecosystems (vLLM, Keel, Nix, etc.).

\textbf{\href{https://github.com/mahmoudk1000/azdo-runner-operator}{AzDO Runner Kubernetes Operator}}\\
\begin{itemize}
	\item Author and maintainer of a Kubernetes operator that provisions and manages on-demand Azure DevOps self-hosted runners as CRDs.
	\item Focus areas: lifecycle safety (admission/mutating/validating webhooks), secure PAT handling, PVC-backed workspaces, and autoscaling runner fleets.
	\item Built Helm charts and CI/CD pipelines for production-grade use.
\end{itemize}

\textbf{\href{https://nixos.org}{Nix \& Nixpkgs}}\\
\begin{itemize}
	\item Long-term reviewer and maintainer in the Nixpkgs ecosystem: package updates, module contributions, reproducibility fixes, and maintainership entries.
	\item Contributed a large number of PRs across packages and modules.
\end{itemize}

% To add more projects, follow this pattern:
% \textbf{\href{URL}{Project Name}} \cite{project-key}\\
% \begin{itemize}
% 	\item Project description and achievements.
% \end{itemize}

% ---------- Education ----------
\cvsection{Education}

\textbf{Alexandria University} \hfill Sep 2019 -- Jun 2023\\
B.Sc. Computer Science \hfill Grade: Good

\vspace{6pt}

\textbf{Information Technology Institute (ITI)} \hfill Jul 2022 -- Aug 2022\\
Linux \& DevOps Engineer Training \hfill Grade: Excellent

% To add more education, follow this pattern:
% \textbf{Institution Name} \hfill Dates\\
% Degree/Program Name \hfill Grade/Achievement \cite{education-key}

% ---------- Certifications ----------
\cvsection{Certifications}
\begin{multicols}{2}
	\begin{itemize}[left=0pt, label={}]
		\item DevOps Engineer — MaharaTech
		\item Linux System Admin — MaharaTech
		\item Linux \& DevOps Training — ITI, Egypt
	\end{itemize}
\end{multicols}

% ---------- Technical Skills ----------
\cvsection{Technical Skills}
\begin{multicols}{3}
	\begin{itemize}[left=0pt, label={}]
		\item Linux
		\item Azure
		\item AWS
		\item Virtualization
		\item Kubernetes
		\item Terraform
		\item Ansible
		\item Nix
		\item Helm
		\item GitHub/Actions
		\item Azure DevOps
		\item Go
		\item Bash
		\item PowerShell
		\item Python
		\item Prometheus
		\item ELK
		\item Git
	\end{itemize}
\end{multicols}

% ---------- Languages ----------
\cvsection{Languages}
\begin{multicols}{3}
	\begin{itemize}[left=0pt, label={}]
		\item Arabic
		\item English
		\item German
	\end{itemize}
\end{multicols}

\printbibliography[heading=none]

\end{document}
